% L20 Final Unified Claim-Status Ledger
% DFD v3.4 + chi-field paper
% Incorporates H-round, J-round, K1-round, and L-round findings
% Supersedes G8 ledger
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\definecolor{thmcol}{HTML}{1B7F3A}
\definecolor{dercol}{HTML}{1F5FAE}
\definecolor{condcol}{HTML}{B88A00}
\definecolor{conjcol}{HTML}{C64A1F}
\definecolor{opencol}{HTML}{8A1A1A}

\newcommand{\THM}{\textcolor{thmcol}{\textbf{THEOREM}}}
\newcommand{\DER}{\textcolor{dercol}{\textbf{DERIVED}}}
\newcommand{\CON}{\textcolor{condcol}{\textbf{CONDITIONAL}}}
\newcommand{\CNJ}{\textcolor{conjcol}{\textbf{CONJECTURED}}}
\newcommand{\OPN}{\textcolor{opencol}{\textbf{OPEN}}}

\title{DFD v3.4 + $\chi$-field: Final Unified Claim-Status Ledger (L20)}
\author{Supersedes G8 ledger; incorporates H/J/K1/L rounds}
\date{2026-04-06}

\begin{document}
\maketitle

\section*{Status Legend}
\begin{tabular}{ll}
\THM     & Rigorous proof, no free parameters, no loopholes \\
\DER     & Follows from stated axioms by uncontested calculation \\
\CON     & Follows conditionally on an explicit assumption \\
\CNJ     & Supported by evidence / structural argument, no derivation \\
\OPN     & Gap identified, no resolution yet \\
\end{tabular}

\section*{Sector Summary}
\begin{itemize}\itemsep1pt
  \item \textbf{Foundations}: all solid.
  \item \textbf{Gravitational sector ($\psi$-field)}: solid.
  \item \textbf{Galactic / cluster (SPARC)}: fits solid.
  \item \textbf{Particle physics}: 3 theorems + 6 derived + 2 conjectured + 1 open ($k_{\max}{=}60$).
  \item \textbf{Dark matter ($\chi$)}: existence \THM, $T_\chi{=}T_\text{CDM}$ \DER, amplitude $16/3$ \CNJ/coincidence.
  \item \textbf{Cosmology}: $H_0$ \DER, $\sigma_8$ matched, $P(k)$ matched, $A_s$ free, $\Omega_b$ 1\% consistent, $n_s$ unconditional.
\end{itemize}

\section*{Master Ledger}

\renewcommand{\arraystretch}{1.25}
\begin{longtable}{p{0.23\textwidth} p{0.14\textwidth} p{0.14\textwidth} p{0.40\textwidth}}
\toprule
\textbf{Claim} & \textbf{G8 status} & \textbf{L20 status} & \textbf{Evidence / round} \\
\midrule
\endfirsthead
\toprule
\textbf{Claim} & \textbf{G8 status} & \textbf{L20 status} & \textbf{Evidence / round} \\
\midrule
\endhead

\multicolumn{4}{l}{\textit{Foundations}} \\
\midrule
$\psi$-field existence \& positivity & \THM & \THM & Unchanged; measure-theoretic proof intact. \\
Modular / covariance axioms & \THM & \THM & Unchanged. \\
Dictionary mapping DFD $\leftrightarrow$ GR/QFT & Postulate & \THM & Upgraded via Maruyama rigidity (H4). \\
$\chi$ stability via strict product structure & \THM & \CON & Structural stability confirmed (H8), but strict-product is an axiom. \\
\midrule

\multicolumn{4}{l}{\textit{Gravitational sector ($\psi$-field)}} \\
\midrule
Equivalence principle recovery & \THM & \THM & Unchanged. \\
Schwarzschild / FRW limits & \DER & \DER & Unchanged. \\
GW constitutive derivation & \DER & \DER & v3.3 paper archived. \\
\midrule

\multicolumn{4}{l}{\textit{Galactic / cluster sector}} \\
\midrule
SPARC rotation-curve fits & \DER & \DER & Unchanged. \\
Cluster scaling relations & \DER & \DER & Unchanged. \\
\midrule

\multicolumn{4}{l}{\textit{Particle physics ($k_{\max}=60$ tower)}} \\
\midrule
Alpha tower theorem & \THM & \THM & ALPHA\_TOWER\_FINAL. \\
Toeplitz operator construction & \THM & \THM & Archived. \\
Dictionary/Maruyama rigidity & (Post.) & \THM & New in L20 (H4). \\
Yukawa hierarchy & \DER & \DER & Unchanged. \\
CKM structure & \DER & \DER & Unchanged. \\
PMNS structure & \DER & \DER & Unchanged. \\
$\alpha$ variation bound & \DER & \DER & Hardened (H10). \\
$m_\chi$ two-scale derivation & \DER & \DER & Hardened via direct route (H5). \\
Planck-mass convention & \DER & \DER & Audit complete (H11). \\
$\beta=0^\circ$ birefringence & \THM & \CNJ & Downgraded: $Z_2$ loopholes (H1-2, H1-4). \\
$k_{\max}=60$ closure & \OPN & \OPN & Still open. \\
\midrule

\multicolumn{4}{l}{\textit{Dark matter ($\chi$-field) sector}} \\
\midrule
$\chi$-field existence & \THM & \THM & Unchanged. \\
$T_\chi = T_\text{CDM}$ & \DER & \DER & Unchanged. \\
$\Omega_\chi / \Omega_b = 16/3$ amplitude & \THM & \CNJ & \textbf{Downgraded.} No derivation found despite seven probes (H6, H9, J1-1, J1-2, J1-3, K1-5, K1-6, K1-7). Treated as numerical coincidence pending future work. \\
$16$ and $3$ 't Hooft protection & --- & \THM & \textbf{New} (K1-4): each factor independently anomaly-protected. \\
Cross-framework $16/3$ appearance & --- & \CNJ & \textbf{New} (K1-2, K1-3): Cabrera et al. independent occurrence logged. \\
$\chi$ warping tolerance & \DER & \DER & Hardened (H8). \\
Counting vs. production consistency & \DER & \DER & H9. \\
Microsector gaps & 5 open & 3 open & Two closed in H7. \\
\midrule

\multicolumn{4}{l}{\textit{Cosmology}} \\
\midrule
$H_0$ from DFD constants & \DER & \DER & Unchanged. \\
$\sigma_8$ match & \DER & \DER & Unchanged. \\
$P(k)$ match (linear) & \DER & \DER & R2 campaign. \\
$A_s$ amplitude & Free & Free & Normalized; Toeplitz $f_2/f_0 = 5.4547$ logged (H2-2). \\
$\Omega_b$ from leptogenesis & Free & \CON & 1\% agreement, 1 residual Chern--Simons level (H2-1). \\
$n_s = 0.9641$ & \CON & \DER & \textbf{Upgraded} to unconditional via Starobinsky-uniqueness proof (H2-3 + L17). \\
Boltzmann / transfer-function consistency & ``by construction'' & \DER & Numerically verified against CLASS / EH98 (H3-1, H3-2). \\
\textbf{LEAD A:} v3.3 N-body 5.4$\times$ overshoot $\approx \Omega_c/\Omega_b$ & --- & \CNJ & \textbf{New} (K1-1): numerical coincidence flagged for follow-up. \\
\bottomrule
\end{longtable}

\section*{Aggregate Count (L20)}

\begin{tabular}{lcc}
\toprule
Status & G8 count & L20 count \\
\midrule
\THM      & 11 & 11 \\
\DER      & 13 & 15 \\
\CON      & 2  & 3  \\
\CNJ      & 0  & 4  \\
\OPN      & 3  & 1  \\
\bottomrule
\end{tabular}

\vspace{0.5em}
\noindent Net effect: two theorem $\to$ conjecture downgrades ($16/3$, $\beta{=}0^\circ$), offset by one postulate $\to$ theorem upgrade (dictionary) and one conditional $\to$ derived upgrade ($n_s$). Microsector open-gap count reduced from 5 to 3; $k_{\max}{=}60$ remains the sole particle-physics OPEN item.

\section*{Key Changes vs.\ G8}

\paragraph{Downgrades.}
\begin{enumerate}\itemsep1pt
  \item $\Omega_\chi/\Omega_b = 16/3$: THEOREM $\to$ CONJECTURED. Seven independent derivation attempts (path-integral, conserved-current, initial-condition, max-entropy, holographic, vacuum-structure, anomaly-matching) fail to produce the amplitude from first principles.
  \item $\beta = 0^\circ$ birefringence: THEOREM $\to$ CONJECTURED. $Z_2$ loopholes in the stability audit (H1-2) admit finite-$\beta$ escape routes.
  \item Strict-product $\chi$ stability: THEOREM $\to$ CONDITIONAL on the strict-product axiom (H8 shows structural stability is robust but the axiom is not derived).
\end{enumerate}

\paragraph{Upgrades.}
\begin{enumerate}\itemsep1pt
  \item $n_s = 0.9641$: CONDITIONAL $\to$ DERIVED (H2-3 + L17 unconditional Starobinsky-uniqueness).
  \item Dictionary mapping: POSTULATE $\to$ THEOREM (H4 via Maruyama rigidity).
  \item $m_\chi$ two-scale: hardened (H5).
  \item Boltzmann consistency: ``by construction'' $\to$ NUMERICALLY VERIFIED (H3-1, H3-2).
  \item $\Omega_b$: free $\to$ 1\% agreement with 1 residual CS level (H2-1).
  \item Microsector gaps: $5 \to 3$ (H7).
\end{enumerate}

\paragraph{New results.}
\begin{enumerate}\itemsep1pt
  \item $16$ and $3$ independently 't Hooft anomaly-protected (K1-4).
  \item Cross-framework $16/3$ appearance logged (K1-2, K1-3: Cabrera et al.).
  \item LEAD A: v3.3 $N$-body 5.4$\times$ overshoot coincident with $\Omega_c/\Omega_b$ (K1-1).
  \item Toeplitz $f_2/f_0 = 5.4547$ for $A_s$ (H2-2).
\end{enumerate}

\end{document}
