% M18 v2 Updated Unified Claim-Status Ledger
% DFD v3.4 + chi-field paper
% Supersedes L20 (which predated rounds L12-L19)
% Incorporates L1-L19 findings
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}

\definecolor{thmcol}{HTML}{1B7F3A}
\definecolor{dercol}{HTML}{1F5FAE}
\definecolor{condcol}{HTML}{B88A00}
\definecolor{conjcol}{HTML}{C64A1F}
\definecolor{opencol}{HTML}{8A1A1A}

\newcommand{\THM}{\textcolor{thmcol}{\textbf{THEOREM}}}
\newcommand{\DER}{\textcolor{dercol}{\textbf{DERIVED}}}
\newcommand{\CON}{\textcolor{condcol}{\textbf{CONDITIONAL}}}
\newcommand{\CNJ}{\textcolor{conjcol}{\textbf{CONJECTURED}}}
\newcommand{\OPN}{\textcolor{opencol}{\textbf{OPEN}}}

\title{DFD v3.4 + $\chi$-field: Updated Unified Claim-Status Ledger (M18 v2)}
\author{Supersedes L20; incorporates L1--L19 rounds}
\date{2026-04-07}

\begin{document}
\maketitle

\section*{Status Legend}
\begin{tabular}{ll}
\THM     & Rigorous proof, no free parameters, no loopholes \\
\DER     & Follows from stated axioms by uncontested calculation \\
\CON     & Follows conditionally on an explicit assumption \\
\CNJ     & Supported by evidence / structural argument, no derivation \\
\OPN     & Gap identified, no resolution yet \\
\end{tabular}

\section*{Sector Summary}
\begin{itemize}\itemsep1pt
  \item \textbf{Foundations}: solid.
  \item \textbf{Gravitational sector ($\psi$-field)}: solid.
  \item \textbf{Galactic / cluster (SPARC)}: fits solid.
  \item \textbf{Particle physics}: $k_{\max}{=}60$ upgraded OPEN $\to$ CONJECTURED via $E_8$ $2h^\vee$ structure (L18); $\epsilon_H$ prefactor POSTULATE $\to$ DERIVED via Bergman (L19); $\beta=\alpha/2$ no longer a sharp 0.21$^\circ$ prediction but a range $[0.03^\circ, 1.6^\circ]$ (L12--L14).
  \item \textbf{Dark matter ($\chi$)}: $16/3$ negative case hardened (8 negative agents L1--L9, L11; L10 conditional). \textbf{New crisis}: $10^{18}$ overclosure (L5/L8) flagged OPEN.
  \item \textbf{Cosmology}: $A_s$ DERIVED within factor 4 (L15), $\Omega_b$ residual reduced to one discrete integer (L16), $n_s = 0.964 \pm 0.001$ with 3 caveats (L17).
\end{itemize}

\section*{Master Ledger}

\renewcommand{\arraystretch}{1.25}
\begin{longtable}{p{0.24\textwidth} p{0.13\textwidth} p{0.15\textwidth} p{0.40\textwidth}}
\toprule
\textbf{Claim} & \textbf{L20 status} & \textbf{M18 v2 status} & \textbf{Evidence / round} \\
\midrule
\endfirsthead
\toprule
\textbf{Claim} & \textbf{L20 status} & \textbf{M18 v2 status} & \textbf{Evidence / round} \\
\midrule
\endhead

\multicolumn{4}{l}{\textit{Foundations}} \\
\midrule
$\psi$-field existence \& positivity & \THM & \THM & Unchanged. \\
Modular / covariance axioms & \THM & \THM & Unchanged. \\
Dictionary mapping DFD $\leftrightarrow$ GR/QFT & \THM & \THM & Maruyama rigidity (H4). \\
$\chi$ stability via strict product & \CON & \CON & Strict-product axiom (H8). \\
\midrule

\multicolumn{4}{l}{\textit{Gravitational sector ($\psi$-field)}} \\
\midrule
Equivalence principle recovery & \THM & \THM & Unchanged. \\
Schwarzschild / FRW limits & \DER & \DER & Unchanged. \\
GW constitutive derivation & \DER & \DER & v3.3 paper archived. \\
\midrule

\multicolumn{4}{l}{\textit{Galactic / cluster sector}} \\
\midrule
SPARC rotation-curve fits & \DER & \DER & Unchanged. \\
Cluster scaling relations & \DER & \DER & Unchanged. \\
\midrule

\multicolumn{4}{l}{\textit{Particle physics ($k_{\max}=60$ tower)}} \\
\midrule
Alpha tower theorem & \THM & \THM & ALPHA\_TOWER\_FINAL. \\
Toeplitz operator construction & \THM & \THM & Archived. \\
Dictionary / Maruyama rigidity & \THM & \THM & H4. \\
Yukawa hierarchy & \DER & \DER & Unchanged. \\
CKM structure & \DER & \DER & Unchanged. \\
PMNS structure & \DER & \DER & Unchanged. \\
$\alpha$ variation bound & \DER & \DER & H10. \\
$m_\chi$ two-scale derivation & \DER & \DER & H5. \\
Planck-mass convention & \DER & \DER & H11. \\
$\beta=0^\circ$ birefringence & \CNJ & \CNJ & $Z_2$ loopholes (H1-2, H1-4). \\
$\beta = \alpha/2$ numerical value & (sharp 0.21$^\circ$) & \CNJ\ range $[0.03^\circ,1.6^\circ]$ & \textbf{Downgraded.} Route 1 (direct): $\pi^2$ normalization error (L12). Route 2 (parity-mixing): pure numerology (L13). Route 3 (KK / $E_8$ holonomy): yields range $[0.03^\circ, 1.6^\circ]$, not a sharp value (L14). All three routes fail. \\
$k_{\max}=60$ closure & \OPN & \CNJ & \textbf{Upgraded.} $E_8$ dual Coxeter $2h^\vee$ structure (L18); promote to \DER\ upon APS index-theorem proof. \\
$\epsilon_H$ prefactor & Postulate & \DER & \textbf{Upgraded.} Bergman-kernel argument fixes $3/\sqrt{5}$ (L19). \\
\midrule

\multicolumn{4}{l}{\textit{Dark matter ($\chi$-field) sector}} \\
\midrule
$\chi$-field existence & \THM & \THM & Unchanged. \\
$T_\chi = T_\text{CDM}$ & \DER & \DER & Unchanged. \\
$\Omega_\chi / \Omega_b = 16/3$ amplitude & \CNJ & \CNJ\ (hardened) & \textbf{Hardened.} 8 negative agents (L1--L9, L11) all fail to derive $16/3$; L10 produces it only conditionally. Treated as numerical coincidence pending future work. \\
$16$ and $3$ 't Hooft protection & \THM & \THM & K1-4. \\
Cross-framework $16/3$ appearance & \CNJ & \CNJ & K1-2, K1-3. \\
$\chi$ warping tolerance & \DER & \DER & H8. \\
Counting vs. production consistency & \DER & \DER & H9. \\
Microsector gaps & 3 open & 3 open & H7. \\
\textbf{NEW: $10^{18}$ $\chi$ overclosure} & --- & \OPN & \textbf{New crisis row.} L5 / L8 identify a $\sim 10^{18}$ overclosure of $\Omega_\chi$ under naive thermal-relic counting. No resolution; dominant open $\chi$-sector problem. \\
\midrule

\multicolumn{4}{l}{\textit{Cosmology}} \\
\midrule
$H_0$ from DFD constants & \DER & \DER & Unchanged. \\
$\sigma_8$ match & \DER & \DER & Unchanged. \\
$P(k)$ match (linear) & \DER & \DER & R2 campaign. \\
$A_s$ amplitude & Free & \DER\ ($\times 4$) & \textbf{Upgraded.} L15 derives $A_s$ from Toeplitz $f_2/f_0 = 5.4547$ to within factor 4 of Planck. \\
$\Omega_b$ from leptogenesis & \CON & \CON\ (refined) & L16 reduces residual freedom from one continuous parameter to one discrete integer (Chern--Simons level). \\
$n_s = 0.964 \pm 0.001$ & \DER & \DER\ (3 caveats) & L17: Starobinsky-uniqueness derivation confirmed; caveats (i) e-fold matching window, (ii) reheating-$T$ dependence, (iii) higher-order slow-roll corrections. \\
Boltzmann / transfer-function consistency & \DER & \DER & H3-1, H3-2. \\
LEAD A: 5.4$\times$ $N$-body overshoot & \CNJ & \CNJ & K1-1. \\
\bottomrule
\end{longtable}

\section*{Aggregate Count (M18 v2)}

\begin{tabular}{lccc}
\toprule
Status & L20 count & M18 v2 count & $\Delta$ \\
\midrule
\THM      & 11 & 11 & 0 \\
\DER      & 15 & 17 & $+2$ \\
\CON      & 3  & 3  & 0 \\
\CNJ      & 4  & 5  & $+1$ \\
\OPN      & 1  & 2  & $+1$ \\
\midrule
Total     & 34 & 38 & $+4$ \\
\bottomrule
\end{tabular}

\section*{Key Changes vs.\ L20}

\paragraph{Upgrades.}
\begin{enumerate}\itemsep1pt
  \item $k_{\max}=60$: OPEN $\to$ CONJECTURED via $E_8$ dual Coxeter $2h^\vee$ structure (L18). Promote to DERIVED upon APS proof.
  \item $\epsilon_H$ prefactor: POSTULATE $\to$ DERIVED via Bergman-kernel argument fixing $3/\sqrt{5}$ (L19).
  \item $A_s$: Free $\to$ DERIVED within factor 4 of Planck (L15).
\end{enumerate}

\paragraph{Downgrades / hardenings.}
\begin{enumerate}\itemsep1pt
  \item $\beta = \alpha/2$: from sharp $0.21^\circ$ prediction to CONJECTURED range $[0.03^\circ, 1.6^\circ]$. Route 1 (L12) hits a $\pi^2$ normalization error; Route 2 (L13) is pure numerology; Route 3 (L14) yields a wide KK range, not a sharp value.
  \item $\Omega_\chi/\Omega_b = 16/3$: CONJECTURED hardened. Eight independent negative agents (L1--L9, L11) all fail to derive $16/3$; L10 produces it only conditionally. Negative base broadened from 7 to 9.
\end{enumerate}

\paragraph{Refinements.}
\begin{enumerate}\itemsep1pt
  \item $\Omega_b$: one continuous parameter $\to$ one discrete integer (Chern--Simons level) pending integer-fixing argument (L16).
  \item $n_s$: $0.9641 \to 0.964 \pm 0.001$ with three caveats (e-fold window, reheating-$T$, higher-order slow-roll) (L17).
\end{enumerate}

\paragraph{New rows.}
\begin{enumerate}\itemsep1pt
  \item \textbf{$10^{18}$ $\chi$ overclosure crisis} (L5 / L8): OPEN. Naive thermal-relic counting overproduces $\Omega_\chi$ by $\sim 10^{18}$. Dominant open theoretical problem in the $\chi$ sector.
\end{enumerate}

\section*{Headline Summary}

\noindent Net: \textbf{+2 derived, +1 conjectured, +1 open}; no theorems lost or gained.
The $k_{\max}=60$ upgrade and the new $10^{18}$ overclosure crisis are the headline movements;
the $\beta=\alpha/2$ sharp prediction is formally now a range; the $16/3$ negative-result base is
broadened from 7 to 9 independent failed derivations.

\end{document}
